---
title: "Summary of Regression Coefficients"
author: "Tim Ballard"
date: "12/5/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
#load libraries
library(rstan)
library(knitr)

#load fit object and extract samples
load(file="../data/derived/fit_vtfB_ratio_reciprocal.RData")
samples = extract(fit)

names = c('intercept','gender (1=f,-1=m)','age','task pairing 2','task pairing 3','PFC greymatter','ratio')


```

# Change in DISCRIMINABILITY from pre to post

Note: discriminability is calculated as the drift rate for the correct response minus the drift rate for the incorrect response.

### ANODAL

```{r echo=FALSE}


COEFS_anodal_diff = samples$COEFS_anodal_v_diff
COEFS_cathodal_diff = samples$COEFS_cathodal_v_diff
COEFS_sham_diff = samples$COEFS_sham_v_diff

#anodal
kable(
  data.frame(lower=apply(COEFS_anodal_diff,2,quantile,0.025),
             mean=apply(COEFS_anodal_diff,2,mean),
             upper=apply(COEFS_anodal_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```

### CATHODAL

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_cathodal_diff,2,quantile,0.025),
             mean=apply(COEFS_cathodal_diff,2,mean),
             upper=apply(COEFS_cathodal_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```

### SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_sham_diff,2,mean),
             upper=apply(COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


### ANODAL VS SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_anodal_diff-COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_anodal_diff-COEFS_sham_diff,2,mean),
             upper=apply(COEFS_anodal_diff-COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


### CATHODAL VS SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,mean),
             upper=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


# Change in THRESHOLD from pre to post

Note: discriminability is calculated as the drift rate for the correct response minus the drift rate for the incorrect response.

### ANODAL

```{r echo=FALSE}


COEFS_anodal_diff = samples$COEFS_anodal_B
COEFS_cathodal_diff = samples$COEFS_cathodal_B
COEFS_sham_diff = samples$COEFS_sham_B

#anodal
kable(
  data.frame(lower=apply(COEFS_anodal_diff,2,quantile,0.025),
             mean=apply(COEFS_anodal_diff,2,mean),
             upper=apply(COEFS_anodal_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```

### CATHODAL

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_cathodal_diff,2,quantile,0.025),
             mean=apply(COEFS_cathodal_diff,2,mean),
             upper=apply(COEFS_cathodal_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```

### SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_sham_diff,2,mean),
             upper=apply(COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


### ANODAL VS SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_anodal_diff-COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_anodal_diff-COEFS_sham_diff,2,mean),
             upper=apply(COEFS_anodal_diff-COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


### CATHODAL VS SHAM

```{r echo=FALSE}

#anodal
kable(
  data.frame(lower=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,quantile,0.025),
             mean=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,mean),
             upper=apply(COEFS_cathodal_diff-COEFS_sham_diff,2,quantile,0.975),
            row.names = names),
      digits=3)

```


